NIRCam Calibration Plan

### 2016-11-24 ms.tex
I added minor updates to the description to the transfer while I wrestle with webbpsf and pynrc for the weird bright source modes.

\section{Ways to Observe Really Bright Stars With NIRCam}

@@

\section{Conclusions}

The James Webb Space Telescope will do unprecedented science with it's great calibration.

>>>>

\clearpage
\section{Transferring to Directly Calibrated Sources}

The primary JWST standards for absolute calibration have been tied to directly calibrated photometric sources through transfers, such as with HST's STIS instrument.
As an independent check on those transfers, NIRCam can be used to observe those directly calibrated sources and transfer from the brightest ($K \sim -1$) sources all the way to the faintest calibrators ($K \sim 16$)
Observing these bright sources (which are bright naked eye stars!) with JWST's NIRCam can be achieved with a combination of narrowband filters, small subarray sizes, a Lyot stop pupil mask (19\% transmission) and a neutral density (ND) filter.
The same configuration can then be used on

\begin{table}
\centering
\caption{Conversion from Directly Calibrated Source to Deep Calibrator}\label{tab:clusterProp}
\begin{tabular}{lrrrrrrr}
\hline \hline
Step		& Source						& Spectral Type	& K Mag		& ND Filter		& Subarray	& Filter  & t$_{exp}$\\
\hline \hline
1		& Direct Calibrator\tablenotemark{a}	& G2 V 			& -1.49		& On	&	32$\times$32	& F466N	& \\
2		& Medium Calibrator				& G2 V			& 12  		& On  &	32$\times$32	& F466N  &  \\
3		& Medium Calibrator				& G2 V			& 6  			& Off &	32$\times$32	& F466N  &  \\
4		& Faint Calibrator				& G2 V			& 16 			& Off &	32$\times$32	& F466N  &  \\
5		& Faint Calibrator				& G2 V			& 16 			& Off &	32$\times$32	& F444W  &  \\
6		& Faint Calibrator				& G2 V			& 16 			& Off &	Full Array  	& F444W  &  \\
\hline
\end{tabular}
\tablenotetext{a}{Any directly calibrated bright source such as the MSX calibrators \citep{price2004msxCal}, Sirius, $\alpha$ Cen A or Vega.}
\vspace{0.05in}
\end{table}

\subsection{Ways to Observe Really Bright Stars With NIRCam}

@@

Sensitivity and saturation limits make use of \texttt{pysynphot} \citep{lim2015pysynphot} with Phoenix stellar models \citep{allard2012phoenix} ranging from 4.0 to 5.0 in log(g).
